Research Cases

### 2025-10-20 Code/R/Research/cases_research.Rmd
4-channel signals with different 3-ranks

## Parameters for mv series (P = 2)
```{r}
P <- 2

@@

# no rates
# rates.true <- matrix(c(0, 0, 0, 0), nrow = P)
# rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), nrow = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), nrow = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), nrow = P)
# rates_case <- "_dsr"
# different by time series rates
# rates.true <- matrix(rep(c(-0.01, -0.02), P), nrow = P)
# rates_case <- "_dtr"
rates.true <- matrix(rep(c(-0.01, -0.02, -0.03, -0.04), P), nrow = P)
rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), nrow = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(c(0, 0, 0, 0), nrow = P)
# freqs_case <- "_nf"
# different by summands freqs
# freqs.true <- matrix(c(0.2, 0.2, 0.22, 0.22), nrow = P)
# freqs_case <- "_dsf"
# different by time series freqs
# freqs.true <- matrix(rep(c(0.2, 0.22), P), nrow = P)
# freqs_case <- "_dtf"
freqs.true <- matrix(rep(c(0.2, 0.22, 0.24, 0.26), P), nrow = P)
freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), nrow = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), nrow = P)
# freqs_case <- "_cdsf"

# equal amplitudes
# A <- matrix(rep(1, P * 2), nrow = P)
# A_case <- "_ea"
A <- matrix(rep(1, P * 4), nrow = P)
A_case <- "_ea"
# different by summands amplitudes 
# A <- matrix(c(1, 2, 1, 2), nrow = P)
# A_case <- "_dsa"
# different by summands, proportional by ts amplitudes 
# A <- matrix(c(1, 2, 3, 6), nrow = P)
# A_case <- "_dspta"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5), nrow = P)
# A_case <- "_da"

# equal phases
# phases.true <- matrix(rep(0, P * 2), nrow = P)
# phases_case <- "_ep"
phases.true <- matrix(rep(0, P * 4), nrow = P)
phases_case <- "_ep"
# different by time series phases
# phases.true <- matrix(c(0, pi / 3, 0, pi / 3), nrow = P)
# phases_case <- "_dtp"

@@

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/four_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

>>>>

## Parameters for mv series (P = 2)
```{r}
P <- 2
P_case = ""

@@

# no rates
rates.true <- matrix(rep(0, P * 2), nrow = P)
rates_case <- "_nr"
# small equal rated
# rates.true <- matrix(c(-0.01, -0.01, -0.01, -0.01), nrow = P)
# rates_case <- "_ser"
# large equal rates
# rates.true <- matrix(c(-0.02, -0.02, -0.02, -0.02), nrow = P)
# rates_case <- "_ler"
# different by summands rates
# rates.true <- matrix(c(-0.01, -0.01, -0.02, -0.02), nrow = P)
# rates_case <- "_dsr"
# different by time series rates
# rates.true <- matrix(rep(c(-0.01, -0.02), P * 2), nrow = P)
# rates_case <- "_dtr"
# rates.true <- matrix(rep(c(-0.01, -0.02, -0.03, -0.01), P), nrow = P)
# rates_case <- "_dtr"
# rates.true <- matrix(rep(c(-0.01, -0.02, -0.03, -0.04), P), nrow = P)
# rates_case <- "_dtr"
# different rates
# rates.true <- matrix(c(-0.01, -0.02, -0.015, -0.025), nrow = P)
# rates_case <- "_dr"

# no freqs
# freqs.true <- matrix(rep(0, P * 4), nrow = P)
# freqs_case <- "_nf"
# all freqs equal
# freqs.true <- matrix(rep(0.2, P * 2), nrow = P)
# freqs_case <- "_ef"
# different by summands freqs
freqs.true <- matrix(rep(c(0.2, 0.22), each = P), nrow = P)
freqs_case <- "_dsf"
# different by time series freqs
# freqs.true <- matrix(rep(c(0.2, 0.22), P * 2), nrow = P)
# freqs_case <- "_dtf"
# freqs.true <- matrix(rep(c(0.2, 0.22, 0.24, 0.2), P), nrow = P)
# freqs_case <- "_dtf"
# freqs.true <- matrix(rep(c(0.2, 0.22, 0.24, 0.26), P), nrow = P)
# freqs_case <- "_dtf"
# different freqs
# freqs.true <- matrix(c(0.2, 0.22, 0.18, 0.24), nrow = P)
# freqs_case <- "_df"
# close different by summands freqs
# freqs.true <- matrix(c(0.02, 0.02, 0.0205, 0.0205), nrow = P)
# freqs_case <- "_cdsf"

# equal amplitudes
A <- matrix(rep(1, P * 2), nrow = P)
A_case <- "_ea"
# different by summands amplitudes 
# A <- matrix(c(1, 2, 1, 2), nrow = P)
# A_case <- "_dsa"
# different by summands, proportional by ts amplitudes 
# A <- matrix(c(1, 2, 3, 6), nrow = P)
# A_case <- "_dspta"
# different amplitudes
# A <- matrix(c(1, 2, 1.5, 2.5, 1.8, 2.3, 2.8, 1.3), nrow = P)
# A_case <- "_da"

# equal phases
# phases.true <- matrix(rep(0, P * 2), nrow = P)
# phases_case <- "_ep"
phases.true <- matrix(rep(0, P * 2), nrow = P)
phases_case <- "_ep"
# different by time series phases
# phases.true <- matrix(c(0, pi / 3, 0, pi / 3), nrow = P)
# phases_case <- "_dtp"

@@

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./Research/comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```
